\chapter{Lesson Learned}

\section{Problems Faced During this Period}

It was tough for me to do six days office from 9:00 AM to 6:00 PM while continuing three other courses. I always tried to give my 100 percent during my internship periods. Collecting the data from the different factories about the sales report, delivery report, production report, inventory issues were a huge trouble for our team. As there were a lot of correction in the data according to the data prodided by the accounts and finance team. It always needed to be two way communication between our ERP in the Gulshan head office and the NTS team (Vendor) in Chittagong to clear all the deadlines set by the top authorities of the company. But there were some communication gap which causes a big trouble to our team to cope up with the deadlines. 

\section{Solution of those Problems}

During my internship period I have gained new knowledges, skills, and met so many new people. I got insights into professional practice and its relative and required skill set. The internship was also good to find out what my strengths and weaknesses are. I learned about Data Analysis, BI Report, BI development, Structures of data etc. Now I know how can make a project successful and what are the requirements. Since, I worked with a ERP team in Union Group which is a combination of IT, Sales executive, Factory Admin, Developer therefore I have gathered a vast knowledge how to work with the team in a Group of company and how to communicate with other team members doing the project work together with time limitations. The most interesting part that I enjoyed and loved to do is meeting with the top authorities of the company and gathering requirements. I also learnt how to solve problems and give a solution feedback.