\chapter{Project as Engineering Problem Analysis}

\section{Sustainability of the Project/Work}

We need to know what is mean by sustainability of the project. It is the ability to maintain and update the system timely. All the software and website need to be maintained and updated.The advantage of oracle fusion ERP is that it is under observation all the time by the vendor and fixes all the bugs immediately when found or complained. The team keeps analyzing the process how to make it easier and convenient to the user and how the time can be saved here rather doing the same task on their previous platform \cite{frazee2012erp}. \\[4ex]
	Moreover the software will be maintained and supported by a NTS team. It will be updated twice in a year according to the requirements of the customer’s needs and all the bugs and problems are regularly updated. \\[4ex]


\section{Social and Environmental Effects and Analysis}
\subsubsection{Social Effects} The main goal of the website was to bring up all the business unit of the company under one website so that the employee could get and process all the information even from home during the pandemic rather than personally visiting the site. It allows the employee to show daily production, manufacture, orders and the delivery. It will become just a matter of few clicks of the mouse button. I short the platform made the task easier for the employee and the stakeholders can look over the financial and sales report from here \cite{niedeggen2014there}. \\[4ex]
\subsubsection{Environmental Effects}
	It’s a high time when the system can plays its best role in the global pandemic of covid-19. The employees can stay at home and continue their job in the system. Only the labors need to be present at the factory to make the production and delivery in real life. The office works can be done here easily. They will find all the information within the comfort of their homes rather than going out in this pandemic \cite{lai2016technology}. \\[4ex]


\section{Addressing Ethics and Ethical Issues }

In the world of smartphones with so much data collection, hacking, cyber-crime, etc. There are some unspoken rules and ethics guidelines that need to be followed when working on creating and releasing an website. The developers made sure there was no breach of conduct and all the points were taken into serious consideration. Some of them are as follows: \\[2ex]

Data Storage: All the data are store in the Oracle cloud. So there is a less risk of data loss due to system failure or disaster.  \\[2ex]

Data Security: Data in the cloud are secured rather than the data's in on premises. There is a less chance to get hacked. A master account is provided to the company to manage other account and give access to the server.  \\[2ex]

Data Storage Security: Only the lead developer has access to the backend server and database. Since they are hosted in the cloud and can only be accessed via the lead developer's login credentials; the data stored can be deemed safe and secure. \\[2ex]








